---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures"
)
library(turingerror)
```

# turingerror

## Overview

Commonly used model accuracy metrics such as Mean Average Error (MAE) and Root Mean Squared Error (RMSE) can produce erroneous results for sparse datasets, i.e., where the amount of information in most items in the dataset is low.

For such datasets it makes more sense to measure prediction errors by comparing predicted and observed values across items. The `turingerror` package includes functions that calculates model prediction errors in this way.


## Installation

Currently the `turingerror` package is available from github.

If you have `devtools` then you can simply run

```{r gh-installation, eval = FALSE}
devtools::install_github("heliopais/turingerror")
```

## Usage

For conversion data you need to supply: 

- a `data.frame` containing the data
- the name of the column in the `data.frame` containing the number of trials per item
- the name of the column in the `data.frame` containing the number of successes per item
- the name of the columns in the `data.frame` (at least 1, but there can be more) containing the predicted conversion per item. Each of these columns corresponds to a different prediction model

You can then call the corresponding Turing Error function with these arguments.  For example:
```{r example-conversion, eval=FALSE}
conversion_turing_error(my_data_frame, 
                        'my_trials_column', 
                        'my_successes_column',
                        'my_predictions_column')
```

