---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# turingerror

The goal of turingerror is to ...

## Installation

You can install turingerror from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("heliopais/turingerror")
```

## Example

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures"
)
library(turingerror)
```

# turingerror

## Overview

Commonly used model accuracy metrics such as Mean Average Error (MAE) and Root Mean Squared Error (RMSE) can produce erroneous results for sparse datasets, i.e., where the amount of information in most records is low.

For such datasets it makes more sense to measure prediction errors across records. The `turingerror` package includes functions that implement 


## Installation

Currently `turingerror` is available from github.

If you have `devtools` then you can simply run

```{r, eval = FALSE}
devtools::install_github("heliopais/turingerror")
```


## Usage
